---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lakeontariospatial

<!-- badges: start -->
<!-- badges: end -->

The goal of lakeontariospatial is to provide common Lake Ontario shapefiles for R users. Shapefiles have been converted to GeoPackage (.gpkg) format using the sf package, ensuring a single-file structure for easier management and integration. Each shapefile was read into R with sf::read_sf() and exported to the package's inst/extdata/ folder using sf::st_write().

## Installation

You can install the development version of lakeontariospatial from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tomgrizz/lakeontariospatial)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(lakeontariospatial)
library(ggplot2)
library(sf)

lake_o <- load_lake_ontario()
ggplot(lake_o) +
  geom_sf()

zones <- lakeontariospatial::load_stocking_zones()
plot(st_geometry(zones))

```

